Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-01-30 CAV 2025 TODO/experiments.tex
exp

\begin{table}[t!]	
	\centering
	\begin{tabular}{|c||c c|c c|c c|c c|}
		\hline
		  & \multicolumn{2}{c|}{45 open ReLUs} & \multicolumn{2}{c|}{50 open ReLUs} 
		  & \multicolumn{2}{c|}{55 open ReLUs} & \multicolumn{2}{c|}{60 open ReLUs}\\ 
		 order & distance & time & distance & time & distance & time & distance & time \\
		\hline \hline
		Gurobi & 0.384 & 252s & &  & & & 0.315  & 306s  \\ 
		SAS (static) & 0.384 & 448s & &  & & & 0.355  & 971s \\
		GS (static) & 0.384 & {\bf 251s} & &  &  & & 0.315 & {\bf 281s} \\ \hline
	\end{tabular}
	\caption{Comparison of different orderings with selection of ReLUs by SAS.}
	\label{table.order}

>>>>

\begin{table}[t!]	
	\centering
	\begin{tabular}{|c||c c|c c|c c|c c|}
		\hline
		  Image 85& \multicolumn{2}{c|}{45 open ReLUs} & \multicolumn{2}{c|}{50 open ReLUs} 
		  & \multicolumn{2}{c|}{55 open ReLUs} & \multicolumn{2}{c|}{60 open ReLUs}\\ 
		 order & distance & time & distance & time & distance & time & distance & time \\
		\hline \hline
		Gurobi & 0.384 & 252s & &  & & & 0.315  & 306s  \\ 
		SAS (static) & 0.384 & 448s & &  & & & 0.355  & 971s \\
		GS (static) & 0.384 & {\bf 251s} & &  &  & & 0.315 & {\bf 281s} \\ \hline
	\end{tabular}
	\caption{Comparison of different orderings with selection of ReLUs by SAS.}
	\label{table.order}
